---
title: "Data606 Project Proposal"
author: "Mahmud Hasan Al Raji"
date: "`r Sys.Date()`"
output: pdf_document
---


# Data Preparation

```{r }
# Load libraries
library(psych)
library(dplyr)
library(ggplot2)

#Getting data
data<-read.csv("https://raw.githubusercontent.com/Raji030/data606_project/main/twitchdata-update.csv",sep=",", header=TRUE)

#Renaming variables
data<-data %>% rename(Stream_time=Stream.time.minutes.,Followers_gained=Followers.gained,Mature_content=Mature)

#Sub-setting data based on mature and non-mature content streaming
mature_no <- data %>% filter(Mature_content =="False")
mature_yes <- data %>% filter(Mature_content == "True")
```

# Research Question 

Does streaming time predict followers gained on Twitch platform?

Does mature content have significant effect on follower gain?

# Cases

Each case represents a Twitch streamer and there are 1000 observations in this data set.

# Data Collection 

This data is collected from a prepared data set via kaggle.com. The data will be stored on my GitHub in order to make the data reproducible.

# Type of Study 

This is an observational study. 

# Data Source

Original: https://www.kaggle.com/datasets/aayushmishra1512/twitchdata

Project Source: https://raw.githubusercontent.com/Raji030/data606_project/main/twitchdata-update.csv

# Dependent Variable

The dependent variable is the follower gained and it is quantitative.

# Independent Variable(s) 

The streaming time (quantitative) and the mature content (qualitative) are the independent variables.

# Relevant summary statistics

Below are the summary statistics for the variables of our consideration:

```{r }
summary(data$Stream_time)
```

```{r}
summary(data$Followers_gained)
```

```{r}
summary(data$Mature_content)
```

```{r }
table(data$Mature_content)
```

```{r}
hist(data$Stream_time)
```

```{r }
# Plotting relationship between Stream_time and Followers_gained
ggplot(data, aes(x =Stream_time, y =Followers_gained)) + geom_smooth()
```

```{r }
# Plotting Stream_time vs Followers_gained data for non-mature content streaming 
ggplot(mature_no, aes(x =Stream_time, y =Followers_gained)) + geom_smooth()

```

```{r }
#Plotting relationship between Stream_time and Followers_gained for mature content streaming
ggplot(mature_yes, aes(x =Stream_time, y =Followers_gained)) + geom_smooth()

```





